---
title: "GGPlot Project"
author: "Olivia & Yulia"
date: '2022-11-22'
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}

#Open libraries

knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(tidyverse)
library(kableExtra)
library(ggthemes)
library(sjmisc)
library(raster)
library(stringr)
library(flexdashboard)
library(paletteer)
library(mgcv)

report2019 <- read.csv("HappinessReport/2019.csv", header = TRUE, sep = ",")
report2018 <- read.csv("HappinessReport/2018.csv", header = TRUE, sep = ",")
report2017 <- read.csv("HappinessReport/2017.csv", header = TRUE, sep = ",")
report2016 <- read.csv("HappinessReport/2016.csv", header = TRUE, sep = ",")
report2015 <- read.csv("HappinessReport/2015.csv", header = TRUE, sep = ",")
report2019$Year <- 2019
report2018$Year <- 2018
report2017$Year <- 2017
report2016$Year <- 2016
report2015$Year <- 2015


selectColumns <- c("Happiness.Rank", "Country",'Happiness.Score', 'Economy..GDP.per.Capita.', 'Family', 'Health..Life.Expectancy.', 'Freedom', 'Generosity', 'Trust..Government.Corruption.', 'Year')

columns <- c('Overall.rank', 'Country.or.region','Score','GDP.per.capita','Social.support','Healthy.life.expectancy','Freedom.to.make.life.choices','Generosity','Perceptions.of.corruption', 'Year')


report2015 <- report2015[,selectColumns]
report2016 <- report2016[,selectColumns]
report2017 <- report2017[,selectColumns]
colnames(report2015) <- columns
colnames(report2016) <- columns
colnames(report2017) <- columns


reportTotal <- rbind(report2016, report2015, report2017, report2018, report2019)

reportTotal <- merge(x=reportTotal,y=ccodes()[,c('NAME','UNREGION1','continent')], 
      by.x=c("Country.or.region"), 
      by.y=c("NAME"),
      all.x=TRUE)



# Update Country Names only for the map graph - reference with report2019a

report2019a <- report2019

report2019a[report2019a$Country.or.region=="United States", "Country.or.region"] <- "USA"
report2019a[report2019a$Country.or.region=="United Kingdom", "Country.or.region"] <- "UK"
report2019a[report2019a$Country.or.region=="Congo (Brazzaville)", "Country.or.region"] <- "Democratic Republic of the Congo"
report2019[report2019a$Country.or.region=="Congo (Kinshasa)", "Country.or.region"] <- "Democratic Republic of the Congo"
report2019a


```

# World Happiness Report {.tabset .tabset-fade}

<!-- comment -->

## Overview

<h2>Index of Happiness in 2019</h2>

The map below represents the happiness index (answers to the Cantril
ladder question) of each country, based on the data collected in 2019.
The most happy countries are shown by the lighter color while the least
happy countries have a darker shade of blue.

**Happiness Index Map, 2019**

```{r map, echo=FALSE, message=FALSE, warning=FALSE}

world_map = map_data("world") %>% 
  filter(! long > 180)

report2019a %>% 
  ggplot(aes(fill = Score, map_id = Country.or.region)) +
  geom_map(map = world_map) +
  expand_limits(x = world_map$long, y = world_map$lat) +
  coord_map("moll") +
  theme_map()

```

By using the map, we can compare the situation between different regions
and have a glance at the countries' indexes. For example, North America
seems to be a happier region than Africa and Ukraine is slightly behind
most other European countries.

<h2>Recognized leaders</h2>

It would be nice to know how to improve the situation into your own
country. Let's look at the examples to follow by determining the leaders
in each category.

```{=html}
<style>

.header{
  text-align: center;
}

</style>
```

<h3 class="header">

Top 3 happiest countries

</h3>

```{r leaders, fig.align='center', echo=FALSE, fig.height=2, warning=FALSE}

#Bring together leaders from each category into one table

score_top3 <- report2019a %>% arrange(desc(Score))
score_top3 <- score_top3 %>% dplyr::select("Country.or.region","Score")
score_top3 <- score_top3[1:3,]

createValueBoxes <- function(df, h = 4, w = 6, padding=0.5, rows = 1){
  
  boxes = nrow(df) # number of items passed
  
# calculate the grid
  cols = 3
    
  df <- data.frame(
      x = rep(seq(0, (w+padding)*cols-1, w+padding), times=rows),
      y = rep(seq(0, (h)*rows-4)),
      h = rep(h, boxes),
      w = rep(w, boxes),
      value = df[[2]],
      info = df[[1]],
      color = factor(1:3)
  )
  
  ggplot(df, aes(x, y, height = h, width = w, label = info)) +
  ## Create the tiles using the `color` column
      geom_tile(aes(fill = color)) +
  ## Add the numeric values as text in `value` column
      geom_text(color = "white", fontface = "bold", size = 10,
                aes(label = value, x = x - 2.9, y = y + 1), hjust = 0) +
  ## Add the labels for each box stored in the `info` column
      geom_text(color = "white", fontface = "bold",
                aes(label = info, x = x - 2.9, y = y - 1), hjust = 0) +
      coord_fixed() +
      scale_fill_brewer(type = "qual",palette = "Dark2") +
  ## Erase the legend
      theme_void() +
      guides(fill = FALSE)
}
createValueBoxes(score_top3)

```

<h3 class="header">

I. GDP per capita

</h3>

```{r gdp, fig.align='center', echo=FALSE, fig.height=2, warning=FALSE}

gdp_top3 <- report2019a %>% arrange(desc(GDP.per.capita))
gdp_top3 <- gdp_top3 %>% dplyr::select("Country.or.region","GDP.per.capita")
gdp_top3 <- gdp_top3[1:3,]

createValueBoxes(gdp_top3)

```

<h3 class="header">

II.Social support

</h3>

```{r social_sup, fig.align='center', echo=FALSE, fig.height=2, warning=FALSE}

socsup_top3 <- report2019a %>% arrange(desc(Social.support))
socsup_top3 <- socsup_top3 %>% dplyr::select("Country.or.region","Social.support")
socsup_top3 <- socsup_top3[1:3,]

createValueBoxes(socsup_top3)

```

<h3 class="header">

III.Healthy life expectancy

</h3>

```{r health, fig.align='center', echo=FALSE, fig.height=2, warning=FALSE}

health_top3 <- report2019a %>% arrange(desc(Healthy.life.expectancy))
health_top3 <- health_top3 %>% dplyr::select("Country.or.region","Healthy.life.expectancy")
health_top3 <- health_top3[1:3,]

createValueBoxes(health_top3)

```

<h3 class="header">

IV.Freedom of choice

</h3>

```{r freedom, fig.align='center', echo=FALSE, fig.height=2, warning=FALSE}

freedom_top3 <- report2019a %>% arrange(desc(Freedom.to.make.life.choices))
freedom_top3 <- freedom_top3 %>% dplyr::select("Country.or.region","Freedom.to.make.life.choices")
freedom_top3 <- freedom_top3[1:3,]

createValueBoxes(freedom_top3)

```

<h3 class="header">

V.Generosity

</h3>

```{r generosity, fig.align='center', echo=FALSE, fig.height=2, warning=FALSE}

generosity_top3 <- report2019a %>% arrange(desc(Generosity))
generosity_top3 <- generosity_top3 %>% dplyr::select("Country.or.region","Generosity")
generosity_top3 <- generosity_top3[1:3,]

createValueBoxes(generosity_top3)

```

<h3 class="header">

VI.Perception of corruption

</h3>

```{r corruption, fig.align='center', echo=FALSE, fig.height=2, warning=FALSE}

corruption_top3 <- report2019a %>% arrange(desc(Perceptions.of.corruption))
corruption_top3 <- corruption_top3 %>% dplyr::select("Country.or.region","Perceptions.of.corruption")
corruption_top3 <- corruption_top3[1:3,]

createValueBoxes(corruption_top3)

```

We can see that the leaders change from category to category. In the
next section the difference between the overall countries' rankings and
their scores in each categories will be even more present. As for now,
we can tell that the happiest country would be probably the with GDP per
capita of Qatar, social support of Iceland, perception of corruption and
health level of Singapore, freedom of choice of Uzbekistan\*, and
generosity of Myanmar. We can also see that the leaders in social
support lead in the overall happiness index as well (even though Denmark
is not at the top-3, it is the fourth).

*\* - As a person from the nearby country I highly question the score of
Uzbekistan in this category. Therefore,I would advise not to use this
list as 100% correct example.*

## Top/bottom analysis

<h2>Comparison between the most happy and the least happy countries</h2>

Do the happiest countries lead in any aspect and wise versa? To find an
answer to this question, let's look at the table below. It includes the
comparison between the top and bottom 10 countries by the Happiness
index (from Finland to Austria and from Haiti to South Sudan).

The best scores overall and for each categories are determined
separately and highlighted by the background colour, where green
represents the best scores and violet represents the worst ones.

```{r topbottom10, echo=FALSE, message=FALSE, warning=FALSE}

topbottomtable <- report2019a[c(1:10, (nrow(report2019a)-9):nrow(report2019a)),]
topbottomtable <- topbottomtable[,(2:9)]


#Create kabble

kbl(topbottomtable, booktabs = T, linesep = "", align = "c", 
    caption = "Distribution of the scores for the best and worst countries", 
    col.names = c("Country", "Happiness index", "GDP per capita", "Social support", "Healthy life expectancy", "Freedom of choice", "Generosity","Perception of corruption")) %>%
  
  kable_styling(full_width = F) %>%
  kable_styling(font_size = 12, position = "center") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  column_spec(3, color = "white", background = spec_color(topbottomtable$Score, end = 0.9, option = "viridis")) %>% 
  column_spec(4, color = "white", background = spec_color(topbottomtable$GDP.per.capita, end = 0.9, option = "viridis")) %>% 
  column_spec(5, color = "white", background = spec_color(topbottomtable$Social.support, end = 0.9, option = "viridis")) %>% 
  column_spec(6, color = "white", background = spec_color(topbottomtable$Healthy.life.expectancy, end = 0.9, option = "viridis")) %>% 
  column_spec(7, color = "white", background = spec_color(topbottomtable$Freedom.to.make.life.choices, end = 0.9, option = "viridis")) %>% 
  column_spec(8, color = "white", background = spec_color(topbottomtable$Generosity, end = 0.9, option = "viridis")) %>% 
  column_spec(9, color = "white", background = spec_color(topbottomtable$Perceptions.of.corruption, end = 0.9, option = "viridis"))


```

One of the most interesting observations that we can make based on this
data is that generosity and perception of corruption are distributed
very differently from all other categories. Haiti, being one of the
worst countries by the Happiness index, is also one of the leaders by
Generosity category. On the other hand, happiest countries usually have
very high GDP, social support, health level, and freedom of choice.

<h2>The difference in happiness level</h2>

We can also take a look at how big the difference in the happiness level
between the general leaders and the outsider is. A comparison is made in
the graph below:

```{r top10, echo=FALSE, message=FALSE, warning=FALSE}

report2019[c(1:10, (nrow(report2019)-9):nrow(report2019)),]  %>% 
  ggplot(aes(x=reorder(Country.or.region,-Score,sum), y=Score, fill = Score)) +
  geom_bar(stat="summary", fun="mean") + 
  coord_flip() +
  geom_hline(yintercept = mean(report2019$Score))




```

It is totally worth noting that the happiest countries are twice as
happy in comparison to the least happy countries. The division is very
high, regardless of inequality in distribution between some categories.

## France

```{r echo=FALSE, message=FALSE, warning=FALSE}

france <- reportTotal[reportTotal$Country.or.region == "France",]

france



```

## Trends

<h2>Countries with the highest progression</h2>

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(flexdashboard)



```

## Continent

trends by continent

```{r echo=FALSE}
reportTotal
```

## Forecasting

# 

```{r}


```
